Describing the C-space of asynchronous periodic task using DIT

### 2013-07-26 dit-paper_ieee.tex
Added numerical example

	Every DIT being an idle instant, the execution of the system after a DIT does
	not depend on the execution before it. Because the synchronous arrival pattern is
	the worst case [citation needed], it is sufficient for the DBF test to only
	consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\

@@

	\subsection{Our work}
		In this paper, we extend the work of \cite{george2009characterization} to the
		asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of
		the concept of DIT adapted to the asynchronous case called first periodic DIT
		($t_d$), along with an algorithm to find its value for any period values. In Section
		\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
		system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is
		sufficient to consider. In section ???, we present a simulation where we find that........

@@

	PAUL PAUL PAUL ?

@@

@@

		\begin{center}
		\begin{tabular}{|r|c|c|c|c|}
		 \hline
		  & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
		 \hline
		 $\tau_1$ & 5 & $C_1$ & 4 & 9\\
		 \hline
		 $\tau_2$ & 0 & $C_2$ & 12 & 14\\
		 \hline
		\end{tabular}
		\end{center}
		~\\

The FPDIT happens at $t=12$ and $H = 126$. The study interval using the FPDIT is thus $[12, 138]$, which contains 261 intervals $[a,d]$ with $a$ being the arrival of a job, $d$ being the deadline of a job, and $12 \leqslant a < d \leqslant 138$. For comparison, the more pessimistic study interval is $[5, 257]$ which yields 1006 intervals.\\

We now apply the

@@

!!! (Sans appliquer le simplexe ou un truc comme ça, si un DIT existe on divisera toujours par 4 le nombre de contraintes ??)

>>>>

	Every DIT being an idle instant, the execution of the system after a DIT does
	not depend on the execution before it. Because the synchronous arrival pattern is
	the worst case [citation needed], it is sufficient for the DBF test to only
	consider intervals $[0, t]$ with $t$ being a deadline before or at the first DIT.\\

@@

	\subsection{Our work}
		In this paper, we extend the work of \cite{george2009characterization} to the
		asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of
		the concept of DIT adapted to the asynchronous case called first periodic DIT
		($t_d$), along with an algorithm to determine its existence and value for any system. In Section
		\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
		system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is
		sufficient to consider. In section ???, we present a simulation where we find that........

@@

	(Paul ?)

@@

(Remarque : Sans appliquer le simplexe ou un truc comme ça, si un DIT existe on divisera toujours par exactement 4 le nombre de contraintes ??)

@@

		\begin{center}
		\begin{tabular}{|r|c|c|c|c|}
		 \hline
		  & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
		 \hline
		 $\tau_1$ & 8 & $C_1$ & 7 & 15\\
		 \hline
		 $\tau_2$ & 0 & $C_2$ & 2 & 5\\
		 \hline
		\end{tabular}
		\end{center}
		~\\

The FPDIT happens at $t=15$ and we have $H = 15$. The study interval using the FPDIT is thus $[15, 30]$, which contains 11 intervals $[a,d]$ with $a$ being the arrival of a job, $d$ being the deadline of a job, and $15 \leqslant a < d \leqslant 30$. Those intervals are
$[15, 17]$, $[15, 22]$, $[15, 27]$, $[15, 30]$, $[20, 22]$, $[20, 27]$, $[20, 30]$, $[23, 27]$, $[23, 30]$, $[25, 27]$ and $[25, 30]$. For comparison, the more pessimistic study interval is $[8, 38]$ which yields 57 intervals.\\

For each $[a, d]$, we have a constraint $$\sum_{i=0}^{n-1} n_i(a, d) \, C_i \leqslant d - a$$ which give a description of the C-space.\\

We now apply algorithm \ref{alg:prunRedun} to remove redundancies, leaving us with the following constraints:
$$
\left\{
	\begin{array}{ccccc}
		& & C_2 & \leqslant & 2 \\
		C_1 & + & C_2 & \leqslant & 7
	\end{array}
\right.
$$
The C-space thus contains 11 points $(C_1, C_2) = (1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(6, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$, $(4, 2)$ and $(5, 2)$.\\

Let us now consider the same system but with a synchronous pattern of arrival.

		\begin{center}
		\begin{tabular}{|r|c|c|c|c|}
		 \hline
		  & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
		 \hline
		 $\tau_1$ & 0 & $C_1$ & 7 & 15\\
		 \hline
		 $\tau_2$ & 0 & $C_2$ & 2 & 5\\
		 \hline
		\end{tabular}
		\end{center}
		~\\

The first DIT happens at time $t_d = 7$. The intervals to consider are thus of the form $[0, t]$ where $t$ is a deadline happening before or at time $t_d$. This yields 2 intervals ($[0, 2]$ and $[0, 7]$) and the following constraints describing the C-space, none of them being redundant:
$$
\left\{
	\begin{array}{ccccc}
		& & C_2 & \leqslant & 2 \\
		C_1 & + & 2 C_2 & \leqslant & 7
	\end{array}
\right.
$$
This time, the C-space only contains 8 points: $(1, 1)$, $(2, 1)$, $(3, 1)$, $(4, 1)$, $(5, 1)$, $(1, 2)$, $(2, 2)$, $(3, 2)$.\\

Fig. \ref{fig:cspaceComp} shows the two C-spaces in the plane.

\begin{figure}[h]
\begin{center}
	\includegraphics[width=0.5\textwidth]{figs/cspace_example.png}
	\caption{C-space of an asynchronous system and its corresponding synchronous system}
	\label{fig:cspaceComp}
\end{center}
\end{figure}

@@
